Using temperature distributions of active regions to investigate flare activity

### 2015-03-12 paper.tex
Edits to include March

\subsection{Active region analysis}
The temperature map method described in \citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February 2011. % And March, hopefully
This month was chosen because several flares occured during this time with a wide range of peak fluxes. % These months
The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare. % Double check these numbers to include March

For each flare event investigated, a temperature map was calculated for a 150 x 150 arcsec area around the corresponding active region at 1-minute intervals for the 30 minutes preceding the start of the flare. % Double check temperature map size
The maximum, 95th percentile, mean, 5th percentile and minimum temperatures were then calculated for each temperature map for each flare in order to compare if and how the bulk temperature of the active regions changed before the flare.
The 95th and 5th percentiles were calculated because the maximum and minimum may be affected by small numbers of unusually high or low temperature pixels, which may not accurately represent how the bulk temperature of the active region changes with time. % Decide if it's worth doing min and max as well as percentiles
Each of these parameters was plotted against time for each active region, and was compared to the peak flux of the flares for all active regions.

@@

% Put this table in an appendix if possible
% Also try and put two sets of columns on a page so it takes up less space
\begin{longtable}{c|c|c}
	\caption{Start times and associated active regions of solar flares studied during 2011-02.}\\ % And March
		Date and time & GOES class & NOAA Active region \\
		\hline
		\input{tempplotsmean/flarelist.txt}
	\label{tab:flares}
\end{longtable}

>>>>

\subsection{Active region analysis}
The temperature map method described in \citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February and March 2011.
These months were chosen because several flares occured during this time with a wide range of peak fluxes.
The flares detected included many small flares (B and C class) as well as several larger M class flares and two X class flares.

For each flare event investigated, a temperature map was calculated for a 150 x 150 arcsec area around the corresponding active region at 1-minute intervals for the 30 minutes preceding the start of the flare.
The maximum, 95th percentile, mean, 5th percentile and minimum temperatures were then calculated for each temperature map for each flare in order to compare if and how the bulk temperature of the active regions changed before the flare.
The 95th and 5th percentiles were calculated because the maximum and minimum may be affected by small numbers of unusually high or low temperature pixels, which may not accurately represent how the bulk temperature of the active region changes with time. % Decide if it's worth doing min and max as well as percentiles
Each of these parameters was plotted against time for each active region, and was compared to the peak flux of the flares for all active regions.

@@

% Put this table in an appendix if possible
% Also try and put two sets of columns on a page so it takes up less space
\begin{longtable}{c|c|c}
	\caption{Start times and associated active regions of solar flares studied during 2011-02 and 2011-03.}\\
		Date and time & GOES class & NOAA Active region \\
		\hline
		\input{tempplotsmean/flarelist.txt}
	\label{tab:flares}
\end{longtable}
